\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[T1]{fontenc}

\RequirePackage{tikz}
\RequirePackage{xcolor}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\classesList}[4]{
	\item\small{
		{#1 #2 #3 #4 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-2pt}\item
	\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{\large#1} & \textbf{\small #2} \\
		\textit{\large#3} & \textit{\small #4} \\
		
	\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[1]{
	\item
	\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
		\small#1 & \\
	\end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
	
	%----------HEADING----------
	
	
	\begin{center}
		{\Huge \scshape Dawood Sarfraz} \\ \vspace{5pt}
		{\Large{Machine Learning Engineer}} \\ \vspace{5pt}
		\small 
		\href{tel:+9203061757838}{\raisebox{-0.1\height}{\faPhone} \underline{{+923061757838}}} ~ 
		\href{mailto:dawoodsarfraz.cs@gmail.com}{\raisebox{-0.2\height}{\faEnvelope} \underline{{dawoodsarfraz.cs@gmail.com}}} ~ 
		\href{https://linkedin.com/in/dawood-sarfraz-0466541b6}{\raisebox{-0.2\height}{\faLinkedin}  \underline{{Dawood Sarfraz}}} ~
		\href{https://dawoodsarfraz.github.io/}{\raisebox{-0.2\height}{\faGlobe} \underline{{Website}}}
		~ 
		\href{https://maps.app.goo.gl/DdjDSuGCuwkG288CA}{\raisebox{-0.2\height}{\faIcon{map-marker-alt}} \underline{{Lahore, Pakistan}}} 
		\vspace{-5pt}
	\end{center}
	
	%-----------OBJECTIVE-----------
	%\section{\textcolor{blue}{OBJECTIVE}}
	%{I am Dawood Sarfraz.}
	
		%-----------EDUCATION-----------
	\section{\textcolor{black}{Education}}
	\resumeSubHeadingListStart
	\resumeSubheading
	{FAST National University of Computer and Emerging Sciences}{}
	{Bachelor in Computer Science }{Sep 2020 - Aug 2024}
	\resumeSubHeadingListEnd
	\vspace{-10pt}
	
	%-----------EXPERIENCE-----------
	\section{\textcolor{black}{Experience}}
	\resumeSubHeadingListStart
\resumeSubheading
  {Freelance}{Jan 2023 – Present}
  {Machine Learning Engineer}{Remote}
  \resumeItemListStart
    \resumeItem{\normalsize{Developed real-time video analytics systems using RTSP-to-WebRTC pipelines for low-latency surveillance and monitoring applications.}}

    \resumeItem{\normalsize{Built object detection and tracking systems using YOLOv10/YOLOv11, DeepSORT, and OpenCV for visual understanding in smart security solutions.}}

    \resumeItem{\normalsize{Implemented OCR pipelines using Tesseract, EasyOCR, and custom deep learning models to extract structured information from scanned documents and ID cards.}}

    \resumeItem{\normalsize{Created LLM-based chatbots and document understanding systems using GPT, LLaMA, and RAG to automate customer support and business operations.}}
  \resumeItemListEnd
\vspace{1em}
\resumeSubheading
  {Deutics Global}{Jan 2025 – July 2025}
  {Associate Machine Learning Engineer}{On-site}
  \resumeItemListStart
  \resumeItem{\normalsize{Developed and optimized a real-time video analytics system by converting RTSP streams to WebRTC for efficient live video processing.}}

    \resumeItem{\normalsize{Implemented advanced tracking algorithms for real-time object tracking across frames, enabling movement monitoring and direction estimation.}}

    \resumeItem{\normalsize{Implemented OCR pipelines using Tesseract, EasyOCR, and custom deep learning models to extract license plate numbers from images and video streams.}}

    \resumeItem{\normalsize{Built and optimized algorithms for wait time estimation, queue detection, speed calculation, and traffic light violation detection to improve traffic efficiency, enforce road regulations, and optimize signal timing.}}

    \resumeItem{\normalsize{Implemented line and zone intrusion detection to monitor restricted areas, enhance security, and enforce access regulations.}}
  \resumeItemListEnd

\vspace{1em}
	
\resumeSubheading
{FAST NUCES}{Sep 2023 – December 2024}
{Machine Learning Engineer (Research Assistant)}{On-site}
\resumeItemListStart
    \resumeItem{\normalsize{Conducted research on skin cancer classification using the HAM10000 dataset, focusing on early detection and diagnosis.}}
    
    \resumeItem{\normalsize{Implemented and evaluated deep neural networks (CNN, NasNet, ShuffleNet) for multi-class skin cancer detection.}}
    
    \resumeItem{\normalsize{Achieved up to 93\% accuracy with NasNet, outperforming CNN (92\%) and ShuffleNet (87\%).}}
    
    \resumeItem{\normalsize{Applied data balancing (RandomOverSampler) and model optimization techniques (batch normalization, dropout, Adamax optimizer) to improve robustness and accuracy.}}
    
    \resumeItem{\normalsize{Demonstrated the potential of advanced neural networks to enhance diagnostic precision and support efficient skin cancer detection solutions.}}
    
    

    \vspace{1em} % Adjust spacing
    \resumeItem{\normalsize{Developed an LSTM-based deep learning model to predict future stock prices using historical market data.}}
    
    \resumeItem{\normalsize{Preprocessed datasets containing features such as opening/closing prices and trading volume, and created training/testing splits for time series forecasting.}}
    
    \resumeItem{\normalsize{Trained and tuned LSTM models with hyperparameters (hidden layers, neurons, learning rate) while applying regularization and dropout to prevent overfitting.}}
    
    \resumeItem{\normalsize{Evaluated model performance using MSE, RMSE, and MAE, and visualized predicted vs. actual stock prices to assess accuracy.}}
    
    \resumeItem{\normalsize{Demonstrated the effectiveness of LSTM networks in capturing long-term dependencies and improving stock price forecasting.}}
    
    \resumeItemListEnd
	
	% Duplicate Entry (if needed for some reason)
	\resumeSubheading
	{Anonymous Tree}{Jun 2023 – Aug 2023}
	{Machine Learning Engineer Intern}{Remote}
	\resumeItemListStart
\resumeItem{\normalsize{Developed a personalized recommendation system using user interaction data (clicks, purchases, ratings) and item metadata to provide tailored product suggestions.}}

\resumeItem{\normalsize{Implemented content-based filtering (TF-IDF, Cosine Similarity), collaborative filtering (user/item-based, SVD, KNN), and a hybrid approach to enhance recommendation accuracy.}}

\resumeItem{\normalsize{Optimized models via hyperparameter tuning (Grid Search, Randomized Search) and evaluated performance using Precision, Recall, F1 Score, and MSE.}}

\resumeItem{\normalsize{Applied cross-validation and continuous feedback loops to ensure model generalization, prevent overfitting, and improve recommendations over time.}}

\resumeItem{\normalsize{Improved user engagement and product discovery by delivering relevant recommendations, leading to higher satisfaction and sales.}}

	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	\vspace{-10pt}
	
	%-----------PROJECTS----------- for uncomment use crtl+t
	\section{\textcolor{black}{Projects}}
	\vspace{-5pt}
	\resumeSubHeadingListStart
	
		
%	\resumeProjectHeading
%	{\textbf{\large{{Road Traffic Analysis}}}
%		\href{https://github.com/Dawoodsarfraz/Road-Traffic-Analysis}{\normalsize{\color{blue} Project Link}}}
%	\resumeItemListStart
%	\resumeItem{\normalsize Developed a real-time traffic analytics system using computer vision to track pedestrian crossings, direction, wait times, and duration, along with vehicle queues, bus wait times, vehicle counting, speed detection, and red light violations. Enables data-driven traffic optimization and safety enforcement.}
%	\resumeItemListEnd
%	\vspace{-15pt}
%	
	%-------------------------------------------------
	
	\resumeProjectHeading
	{\textbf{\large{Skin Cancer Classification using NasNet and ShuffleNet}}} 
	\resumeItemListStart
	\resumeItem{\normalsize{Developed deep learning models (Custom CNN, NasNet, ShuffleNet) for multi-class skin cancer classification using the HAM10000 dataset. Enhanced accuracy with batch normalization, dropout, and Adamax optimizer, achieving the highest accuracy with NasNet and improved efficiency with ShuffleNet.}}
	\resumeItemListEnd
	\vspace{-15pt}

	%----------------------------------------

	\resumeProjectHeading
	{\textbf{\large{{LlamaAssist }}}\href{https://github.com/Dawoodsarfraz/LlamaAssist}{\normalsize{\color{blue} Project Link}}}
	\resumeItemListStart
	\resumeItem{\normalsize LLama Assist is an AI-powered application built with LLama 3.2 3B and LLama 3.2 Vision. It allows users to generate assignments with customizable output length and difficulty, save content into text files, and interact with images via AI-driven chat. Perfect for creating and managing assignments with ease and precision.}
	\resumeItemListEnd
	\vspace{-15pt}
		
		%-----------------------------------
	
		\resumeProjectHeading
	{\textbf{\large{{RoboText Classifier }}}\href{https://github.com/Dawoodsarfraz/RoboText-Classifier}{\normalsize{\color{blue} Project Link}}}
	\resumeItemListStart
	\resumeItem{\normalsize Built a text classification model using RoBERTa and NLTK. Enhanced performance with dynamic masking, sentence packing, byte-level BPE vocabulary, and larger batch sizes for efficient, accurate classification of diverse text.}
	\resumeItemListEnd
	\vspace{-15pt}
	
	%-------------------------------------
	
	\resumeProjectHeading
	{\textbf{\large{{Duplicate Questions Pair }}}\href{https://github.com/Dawoodsarfraz/duplicate-questions-pair}{\normalsize{\color{blue} Project Link}}}
	\resumeItemListStart
	\resumeItem{\normalsize Built a model to identify and detect duplicate question pairs using Random Forest, XGBoost, and Decision Tree classifiers. Achieved 90\% accuracy with XGBoost classifier.}
	\resumeItemListEnd
	\vspace{-15pt}
	
	%----------------------------------------
    
%-----------PROGRAMMING SKILLS-----------
\section{\textcolor{black}{Skills}}
\begin{itemize}[leftmargin=0.01in, label={}]
\item{
    \textbf{\normalsize{Programming Languages:}} \normalsize{Python, C++, JavaScript} \\[2pt]

    \textbf{\normalsize{Full-Stack Web Technologies:}} 
    \normalsize{HTML, CSS, Bootstrap, React, FastAPI, Django, Flask, Streamlit, Gradio} \\[2pt]

    \textbf{\normalsize{Tools \& Platforms:}} \normalsize{Git, Docker, AWS} \\[2pt]
    
    \textbf{\normalsize{Databases \& Vector Stores:}} 
    \normalsize{MySQL, MongoDB, FAISS, Pinecone, Weaviate} \\[2pt]

    \textbf{\normalsize{ML/DL Frameworks:}} 
    \normalsize{PyTorch, TensorFlow, Keras, Hugging Face Transformers, YOLO} \\[2pt]

    \textbf{\normalsize{ML/DL Libraries:}} 
    \normalsize{scikit-learn, NumPy, Pandas, Matplotlib, Seaborn, SciPy, OpenCV, NLTK, spaCy} \\[2pt]
    
    \textbf{\normalsize{GenAI Libraries \& Tools:}} 
    \normalsize{LangChain, LlamaIndex, Crew AI} \\[2pt]

    \textbf{\normalsize{LLM Models:}} 
    \normalsize{LLaMA, DeepSeek, Mistral, Falcon, Phi, Qwen, Granite, Gemma} \\[2pt]
    
    \textbf{\normalsize{Speech \& Multimodal Models:}} 
    \normalsize{Whisper} \\[2pt]
    
    \textbf{\normalsize{Techniques:}} 
    \normalsize{Retrieval-Augmented Generation (RAG), Prompt Engineering, Fine-tuning, LoRA, QLoRA, Quantization, Model Distillation, PEFT} \\
}

\end{itemize}
\vspace{-10pt}


    
	
	\resumeSubHeadingListEnd
% 	%-----------PROJECTS-----------
% \section{\textcolor{black}{Certifications}}
% \vspace{-1pt}

%  	\noindent
%  	\href{https://example.com/certificate1}{Tensorflow} \quad
%  	\href{https://example.com/certificate2}{deep learning for Data Science} \quad
%  	\href{https://example.com/certificate3}{Certificate Name 3} \quad
%  	\href{https://example.com/certificate4}{Certificate Name 4}


\end{document}
